### 2023-03-21 main.tex
fix

In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e. a dynamic in which a maximum amount of particles can be present in each site at each time. We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$. Particle of any species can exchange their position in the graph, under this exclusion constraint. The system will be put out of equilibrium and some absorbing duality result are investigated. Moreover, we will use this duality, to study the out of equilibrium steady state. In particular, in case of $\twoj=1$ we should retrieve the model studied in \cite{vanicat2017exact}. We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

@@

We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA states the form of the steady state in function of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relation simpler, and allows to find the steady state of a transformed Hamiltonian, that will be denoted by $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section \ref{sectionDuality}. 

@@

In subsection \ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability. When the maximal occupation of each site $\nu>1$, this nice property is lost. However, something about correlations can be said using duality. In this subsection we still consider the same geometry of \ref{subsection-exact}. As pointed out in section \ref{sectionDuality}, the dual process voids the chain. Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below. In this context it is better to work agin with generators. We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry. \\

@@

where the duality matrix $D$ is again \eqref{dualityMatrix}. Following subsection \ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$. This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

Therefore, arguing similarly to subsection \ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.

>>>>

In this work we concentrate our effort in this last "single layer" case with a repulsive process, i.e. a dynamic in which a maximum amount of particles can be present in each site at each time. We will call this amount, the "maximal occupancy" and it will indicated with $\twoj$ where $\twoj\in\mathbb{N}$. Particle of any species can exchange their position in the graph, under this exclusion constraint. The system will be put out of equilibrium and some absorbing duality result are investigated. Moreover, we will use this duality, to study the out of equilibrium steady state. In particular, in case of $\twoj=1$ we retrieve the model studied in \cite{vanicat2017exact}. We will then exploit this last result and the duality, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

@@

We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA states the form of the steady state in function of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relation simpler, and allows to find the steady state of a transformed Hamiltonian, that will be denoted by $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. \com{clarify}

@@

In subsection~\ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability. When the maximal occupation of each site $\nu>1$, this nice property is lost. However, something about correlations can be said using duality. In this subsection we still consider the same geometry of \ref{subsection-exact}. As pointed out in section~\ref{sectionDuality}, the dual process voids the chain. Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below. In this context it is better to work agin with generators. We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry. \\

@@

where the duality matrix $D$ is again \eqref{dualityMatrix}. Following subsection~\ref{subsectionDualityProof}, to prove \eqref{DualityRelationRD} we only need tho show that the operator $S_{x,y}$ defined in \eqref{symmetry} commutes with $\sum_{i=1}^{N}H_{x,y}^{i}$ and with $H_{x,y}^{m}$. This result will follow from the commutator between $\sum_{i=1}^{N}H_{x,y}^{i}$ and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$ and from the commutator between  and $\sum_{a=2}^{N}(E_{a1}^{x})\otimes \sum_{b=2}^{N}E_{b,1}^{x}$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

Therefore, arguing similarly to subsection~\ref{subsectionDualityProof}, \eqref{DualityRelationRD} can be proved.
